A saturation model for impaired learning with enhanced plasticity

### 2013-07-13 MHCslides/MHCslides.tex
fixed some errors

\begin{frame}{Simplifying assumptions}
%
\begin{itemize}
  \item No spatial/temporal correlations in plasticity events.
      %
      \note[item]{allows us to concentrate on synapse, not neuron/network}
      %
%  \item Which synapses eligible for plasticity chosen randomly.
      %
      \note[item]{No filing system}
      %
  \item Potentiating/depressing plasticity events $\sim$ Poisson processes.% with rates $rf\potdep$, where $f\pot+f\dep=1$.
      %
      \note[item]{don't care if STDP...}
%      %
%      \note[item]{$r=$ total rate of plasticity events per synapse, $f\potdep=$ fraction of events that are potentiating/depressing.}
      %
  \item Potentiation and depression are described by Markov processes.% with transition probabilities $\M\potdep$.
%      %
%      \note[item]{matrix elements: transition prob from $i\to j$, given pot/dep}
%  \item Ideal observer: read weights directly.
%      \note[item]{not electrical activity: don't model neurons/network}
%      \note[item]{upper bound on electrical activity readout}
%      %
%  \item Synaptic weights can only take values $\pm1$.
%      %
%      \note[item]{looks like binary synapse from outside. Inside...}
      %
  \citerr{Fusi2005cascade,Fusi2007multistate,Barrett2008discrete}
\end{itemize}
%
\end{frame}

@@

\begin{frame}{Serial synapse: initial distributions}
%
 %
 \begin{center}
 \begin{tabular}{ccc}
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_wt_wo.svg}}
   & \alignmid{\includegraphics[height=0.05\linewidth]{right_good.svg}} &
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_ko_wo.svg}}
   \\[1.5cm] \alignmid{\includegraphics[height=0.05\linewidth]{down_good.svg}}
   && \alignmid{\includegraphics[height=0.05\linewidth]{up_good.svg}}\\[0.5cm]
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_wt_w.svg}}
   & \alignmid{\includegraphics[height=0.05\linewidth]{left_good.svg}} &
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_ko_w.svg}}
 \end{tabular}
 \end{center}
 %
 \note[item]{WT: start with everything equal -- just for illustration, not essential}
 \note[item]{WT: during training, increase $f\dep$ (green arrow) $\to$ weakening.}
 \note[item]{KO: inc $q\pot\to$ bias, now exponential}
 \note[item]{KO: comp. between inc prob trans \& dec prob ready, now only at bndry}
 \note[item]{KO: second one wins, now exponential}
 \note[item]{pre: reduces/reverses bias.}
 \note[item]{pre: little reverse bias repopulates bndry, helps.}
 \note[item]{pre: too much reverse bias moves away from bndry, hurts.}
 \note[item]{maths next slide}
%
\end{frame}

@@

\begin{frame}{Mathematical explanation}
%
 Serial synapse: $\eq_i \sim \CN \prn{\frac{q\pot}{q\dep}}^i$.

@@

\begin{frame}{Essential features}
%
 The success of the serial model relies on two features:
 \begin{itemize}
   \item Enhancing the effect of saturation,
   \note[item]{due to exponential decay}
   \item Metaplasticity -- repeated potentiation makes subsequent depression harder.
   \note[item]{push away from boundary where signal generated}
 \end{itemize}
 %
 \begin{center}
   \includegraphics[width=0.4\linewidth]{serial.svg}
 \end{center}
 %
 \note[item]{borne out by other models that fail/succeed}
%
\end{frame}

>>>>

\begin{frame}{Simplifying assumptions}
%
\begin{itemize}
  \item No spatial/temporal correlations in plasticity events.
      %
      \note[item]{allows us to concentrate on synapse, not neuron/network}
      %
%  \item Which synapses eligible for plasticity chosen randomly.
      %
      \note[item]{No filing system}
      %
  \vp\item Potentiating/depressing plasticity events $\sim$ Poisson processes.% with rates $rf\potdep$, where $f\pot+f\dep=1$.
      %
      \note[item]{don't care if STDP...}
%      %
%      \note[item]{$r=$ total rate of plasticity events per synapse, $f\potdep=$ fraction of events that are potentiating/depressing.}
      %
  \vp\item Potentiation and depression are described by Markov processes.% with transition probabilities $\M\potdep$.
%      %
%      \note[item]{matrix elements: transition prob from $i\to j$, given pot/dep}
%  \item Ideal observer: read weights directly.
%      \note[item]{not electrical activity: don't model neurons/network}
%      \note[item]{upper bound on electrical activity readout}
%      %
%  \item Synaptic weights can only take values $\pm1$.
%      %
%      \note[item]{looks like binary synapse from outside. Inside...}
      %
  \vp\citerr{Fusi2005cascade,Fusi2007multistate,Barrett2008discrete}
\end{itemize}
%
\end{frame}

@@

\begin{frame}{Serial synapse: initial distributions}
%
 %
 \begin{center}
 \begin{tabular}{ccc}
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_wt_wo.svg}}
   & \alignmid{\includegraphics[height=0.05\linewidth]{right_good.svg}} &
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_ko_wo.svg}}
   \\[1.5cm] \alignmid{\includegraphics[height=0.05\linewidth]{down_good.svg}}
   && \alignmid{\includegraphics[height=0.05\linewidth]{up_good.svg}}\\[0.5cm]
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_wt_w.svg}}
   & \alignmid{\includegraphics[height=0.05\linewidth]{left_good.svg}} &
   \alignmid{\includegraphics[height=0.19\linewidth]{serial_bar_ko_w.svg}}
 \end{tabular}
 \end{center}
 %
 \note[item]{Now only get signal from crossing boundary}
 \note[item]{KO: inc $q\pot\to$ bias, now exponential}
 \note[item]{KO: prob ready wins over prob trans, now exponential}
 \note[item]{pre: reduces/reverses bias.}
 \note[item]{pre: little reverse bias repopulates bndry, helps.}
 \note[item]{pre: too much reverse bias moves away from bndry, hurts.}
 \note[item]{maths next slide}
%
\end{frame}

@@

\begin{frame}{Mathematical explanation}
%
 %
 \begin{center}
   \includegraphics[width=0.4\linewidth]{serial_label.svg}
 \end{center}
 %
 \vp Serial synapse: $\eq_i \sim \CN \prn{\frac{q\pot}{q\dep}}^i$.

@@

\begin{frame}{Essential features}
%
 %
 \begin{center}
   \includegraphics[width=0.4\linewidth]{serial.svg}
 \end{center}
 %
 \vp The success of the serial model relies on two features:
 \begin{itemize}
   \item Enhancing the effect of saturation,
   \note[item]{due to exponential decay}
   \item Metaplasticity -- repeated potentiation makes subsequent depression harder.
   \note[item]{push away from boundary where signal generated}
 \end{itemize}
 \note[item]{borne out by other models that fail/succeed}
%
\end{frame}
